Cell Decomposition of Rank 2 Quiver Grassmannians

### 2017-09-27 Grassmannian_cells.tex
Unknown edits

\noindent Denote by $K(n)$ the \emph{$n$-Kronecker quiver} $1\stackrel{n}{\longleftarrow}2$ with vertices $K_0(n)=\{1,2\}$ and $n$ arrows from vertex $2$ to vertex $1$. 
Write $\Sigma_1$ and $\Sigma_2$ for the BGP-reflection functors of $K(n)$ \cite{bgp}. 
Note that (up to relabeling vertices) the quiver $K(n)$ itself does not change when applying the reflection functors and thus we view them as endofunctors acting on the category $\rep K(n)$ of finite-dimensional representations. %, but the vertices $1$ and $2$ are exchanged. 
With this identification of $K(n)$ and $K(n)^{op}$, the endofunctors $\Sigma_1\Sigma_2$ and $\Sigma_2\Sigma_1$ are each naturally isomorphic to the identity.
%Let $$\Sigma:=\begin{cases}\Sigma_1\text{ if vertex }1 \text{ is a source;}\\\Sigma_2\text{ if vertex }$2$ \text{ is a source.}\end{cases}$$

Define Chebyshev polynomials $u_k$ for $k\in\ZZ$ by the recursion $u_0=0$, $u_1=1$, $u_{k+1}=nu_k-u_{k-1}$.
\begin{theorem}
  For each $m\ge1$, there exist unique (up to isomorphism) indecomposable rigid representations $P_m$ and $I_m$ of $K(n)$ with dimension vectors $(u_m,u_{m-1})$ and $(u_{m-1},u_m)$ respectively. 
  Moreover, any rigid representation of $K(n)$ is isomorphic to one of the form $P_m^{a_1}\oplus P_{m+1}^{a_2}$ or $I_m^{a_1}\oplus I_{m+1}^{a_2}$ for some $m\ge1$ and some $a_1,a_2\ge0$.
\end{theorem}
The representations $P_m$ are called the \emph{preprojective} representations of $K(n)$ and the representations $I_m$ are called \emph{preinjective}.
\begin{remark}
  These representations satisfy the following recursions using the reflection functors:
  \[P_1=S_1,\quad P_m=\Sigma_2 P_{m-1},\quad I_1=S_2,\quad I_m=\Sigma_1 I_{m-1}\]
  for $m\ge2$.
\end{remark}

@@

%\begin{lemma}
%  For any $m\ge1$, we have 
%  \[\dim\Hom(P_m,P_m)=1,\quad \dim\Hom(P_m,P_{m+1})=n,\quad \dim\Hom(P_{m+1},P_m)=0, \quad\dim\Ext(P_{m+1},P_m)=0.\]  
%  Moreover, for $1\le k<n$ and linearly independent functions $f_1,\ldots,f_k\in\Hom(P_m,P_{m+1})$, the map $[f_1\ \cdots\ f_k]:P_m^k\to P_{m+1}$ is injective. 
%\end{lemma}
%\begin{proof} 
%  Note that we have an Auslander-Reiten sequence
%  \begin{equation}
%    \label{eq:AR sequence}
%    0\longrightarrow P_{m-1}\stackrel{\iota_{m-1}}{\longrightarrow} P_m^n\stackrel{[f_1\ \cdots\ f_n]}{\longrightarrow} P_{m+1}\longrightarrow 0
%  \end{equation}
%  with irreducible homomorphisms $f_i$ which are also linearly independent. 
%  Thus they do not factor through a representation $Z\neq P_{m}$ which already means that they are injective, see for instance \cite[Lemma 1.6]{ass}. 
%  If we pick $k<n$ linearly independent homomorphisms $f_{i_1},\ldots, f_{i_k}$, this also means that $[f_{i_1}\ \cdots\ f_{i_k}]:P_m^k\to P_{m+1}$ is injective. 
%  Indeed otherwise, at least one of the homomorphisms would be forced to factor through a representation $Z\neq P_{m}$.
%\end{proof}
%\begin{remark}
%  Fix a basis $\{f_{m,1},\ldots,f_{m,n}\}$ for $\Hom(P_m,P_{m+1})$, $m\ge2$.
%  Define a basis $\{f_{\ell,1},\ldots,f_{\ell,n}\}$ for each $\Hom(P_\ell,P_{\ell+1})$, $1\le\ell\le m-1$, by downward induction as follows.  
%  Write $\iota_\ell:P_\ell\to P_{\ell+1}^n$ for the left-hand morphism from the sequence \eqref{eq:AR sequence} computed using $f_k=f_{\ell+1,k}$, $1\le k\le n$. 
%  Then the basis element $f_{\ell,k}$ is given by composing $\iota_\ell$ with the coordinate projection $\pi_k:P_{\ell+1}^n\to P_{\ell+1}$ onto the $k$-th factor.
%  Indeed, applying $\Hom(-,P_{\ell+1})$ to this sequence \eqref{eq:AR sequence} gives an isomorphism $\Hom(P_{\ell+1}^n,P_{\ell+1})\cong\Hom(P_\ell,P_{\ell+1})$ whereby the natural basis of coordinate projections on the left is taken to the basis $\{f_{\ell,k}\}$ on the right.
%\end{remark}
\begin{corollary}
  \label{cor:preprojective homomorphism duality}
  The sequence \eqref{eq:AR sequence} gives rise to an isomorphism $H_m^*\cong H_{m-1}$.
\end{corollary}
\begin{proof}
  Define a map $\Theta:H_m^*\to H_{m-1}$ by $\Theta(\varphi)=(id\overline{\otimes}\varphi)\circ\iota_{m-1}$, in words $\Theta(\varphi)$ acts on $x\in P_{m-1}$ by contracting with the second factor in $\iota_{m-1}(x)$ to give an element of $P_m$.
  Suppose $\varphi\in H_m^*$ is a nonzero functional on $H_m$ and let $V\subsetneq H_m$ denote the kernel of $\varphi$.
  Then $\Theta(\varphi)=0\in H_{m-1}$ if and only if the image of $\iota_{m-1}$ is contained in $P_m\otimes V\subsetneq P_m\otimes H_m$.
  But then Lemma~\ref{le:injective evaluation maps} implies $\iota_{m-1}$ is the zero map, a contradiction.
  Thus $\Theta:H_m^*\to H_{m-1}$ must be injective and hence an isomorphism.
\end{proof}
\begin{remark}
  The set $Gr(H_m)$ is naturally a poset and Corollary~\ref{cor:preprojective homomorphism duality} gives an identification of the opposite poset $Gr(H_m)^{op}\cong Gr(H_m^*)$ with $Gr(H_{m-1})$.
  We write $\bar{V}\subset H_{m-1}$ for the subspace corresponding to $V\subset H_m$ under this identification.
  Under the isomorphism of $H_{m-1}$ with $H_m^*$, we have $\bar{V}=(H_m/V)^*$.
\end{remark}

@@

\begin{lemma}
  \label{le:unique truncated extension}
  For $V\in Gr(H_m)$, $m\ge2$, the space $\Ext(P_{m+1}^V,P_{m-1})$ is one-dimensional and spanned by the extension
  \begin{equation}
    \label{eq:unique extension}
    \xymatrix{0 \ar[r] & P_{m-1} \ar[r]^(.375){\kappa_V} & P_m\otimes(H_m/V) \ar[r] & P_{m+1}^V \ar[r] & 0}.
  \end{equation}
\end{lemma}
\begin{proof}
  Applying the functor $\Hom(-,P_{m-1})$ to the sequence \eqref{eq:truncated preprojectives} gives an isomorphism $\Ext(P_{m+1}^V,P_{m-1})\cong\Ext(P_{m+1},P_{m-1})$ with a one-dimensional space.
  Writing $X$ for the unique extension of $P_{m+1}^V$ by $P_{m-1}$, this isomorphism gives rise to the following pullback diagram:
  \[\xymatrix{ & & 0 \ar[d] & 0\ar[d] & \\
    & & P_m\otimes V \ar@{=}[r]\ar[d] & P_m\otimes V\ar[d] & \\
    0 \ar[r] & P_{m-1} \ar@{=}[d]\ar[r]^(.425){\iota_{m-1}} & P_m\otimes H_m \ar[r]\ar[d]\ar@{}[dr]|(.7){\lrcorner} & P_{m+1} \ar[r]\ar[d] & 0\\
    0 \ar[r] & P_{m-1} \ar[r]^{\kappa_V} & X \ar[r]\ar[d] & P_{m+1}^V \ar[r]\ar[d] & 0\\
    & & 0 & 0 & }\]
  from which we immediately obtain the isomorphism $X\cong P_m\otimes(H_m/V)$.
\end{proof}
\begin{corollary}
  Suppose $V\in Gr(H_m)$ has codimension one in $H_m$.  Then $P_{m+1}^V\cong P_m^{\bar{V}}$.
\end{corollary}
\begin{proof}
  By Lemma~\ref{le:unique truncated extension}, we have the exact sequence
  \[\xymatrix{0 \ar[r] & P_{m-1} \ar[r]^(.35){\kappa_V} & P_m\otimes(H_m/V) \ar[r] & P_{m+1}^V \ar[r] & 0}.\]
  But $H_m/V$ is a one-dimensional vector space and so $P_m\otimes(H_m/V)\cong P_m$.
  Under this identification, the left hand morphism $\kappa_V$ in the sequence above identifies with a generator of $\bar{V}$ and thus $P_{m+1}^V\cong P_m^{\bar{V}}$.
\end{proof}

@@

  Applying the functor $\Hom(-,P_m^{\bar{W}})$ to the sequence \eqref{eq:AR sequence} we get an exact sequence 
  \[\xymatrix{0 \ar[r] & \Hom(P_{m+1},P_m^{\bar{W}}) \ar[r] & \Hom(P_m\otimes H_m,P_m^{\bar{W}}) \ar[r] & \Hom(P_{m-1},P_m^{\bar{W}}) \ar[r] & 0}.\]
  By Lemma~\ref{le:basic homological properties}, the middle space above is isomorphic to $H_m^*$ and thus $\Hom(P_{m+1},P_m^{\bar{W}})$ can be identified with the kernel of the natural map $H_m^*\to W^*$, i.e.\ with the space $(H_m/W)^*$.
\end{proof}
\begin{corollary}
  For $V,W\in Gr(H_m)$, $m\ge2$, we have natural isomorphisms 
  \[\Hom(P_{m+1}^V,P_m^{\bar{W}})\cong\big(H_m/(V+W)\big)^*\quad\text{and}\quad\Ext(P_{m+1}^V,P_m^{\bar{W}})\cong(V\cap W)^*.\]
\end{corollary}
\begin{proof}
  Applying the functor $\Hom(-,P_m^{\bar{W}})$ to the sequence \eqref{eq:truncated preprojectives} we get an exact sequence
  \[\xymatrix{0 \ar[r] & \Hom(P_{m+1}^V,P_m^{\bar{W}}) \ar[r] & \Hom(P_{m+1},P_m^{\bar{W}}) \ar[r] & \Hom(P_m\otimes V,P_m^{\bar{W}}) \ar[r] & \Ext(P_{m+1}^V,P_m^{\bar{W}}) \ar[r] & 0}.\]
  By Lemma~\ref{le:more truncated homomorphisms}, we may identify $\Hom(P_{m+1}^V,P_m^{\bar{W}})$ and $\Ext(P_{m+1}^V,P_m^{\bar{W}})$ with the kernel and cokernel of the natural map $(H_m/W)^*\to V^*$.
  The result immediately follows from this.
\end{proof}
\begin{remark}
  It is slightly easier to understand the dual of the diagram figuring in the proof above, in particular it is immediate that the kernel of the natural morphism $V\to H_m/W$ is $V\cap W$ while the cokernel of this morphism is $H_m/(V+W)$.
\end{remark}

Let $\tau:\rep K(n)\to\rep K(n)$ denote the Auslander-Reiten translation.
\begin{lemma}
  For $m\ge2$ and $V\in Gr(H_m)$, the Auslander-Reiten translate of the truncated preprojective $P_{m+1}^V$ is again a truncated preprojective representation of $K(n)$.  More precisely, we have $\tau(P_{m+1}^V)=P_{m-1}^{\bar{\bar{V}}}$.
\end{lemma}
\begin{proof}
  Under the Auslander-Reiten translation, the subspace $V\subset H_m$ is taken to a subspace $\tilde V\subset H_{m-2}$ of the same dimension.
  It follows that the evaluation morphism $P_m\otimes V\stackrel{ev_V}{\longrightarrow} P_{m+1}$ transforms via $\tau$ to the evaluation morphism $P_{m-2}\otimes\tilde V\stackrel{ev_{\tilde V}}{\longrightarrow} P_{m-1}$.
  Thus the sequence \eqref{eq:truncated preprojectives} transforms via $\tau$ to the exact sequence
  \[0\longrightarrow P_{m-2}\otimes \tilde V\stackrel{ev_{\tilde V}}{\longrightarrow} P_{m-1}\stackrel{\pi_{\tilde V}}{\longrightarrow} P_{m-1}^{\tilde V}\longrightarrow 0.\]
  This proves the first claim.

@@

\begin{lemma}
  \label{le:truncated exact sequences}
  For $V\in Gr(H_m)$, $m\ge2$, each nontrivial direct sum decomposition $V=U\oplus W$ gives rise to an exact sequence
  \[\xymatrix{0 \ar[r] & P_{m+1} \ar[r] & P_{m+1}^U\oplus P_{m+1}^W \ar[r] & P_{m+1}^V \ar[r] & 0}\]
  representing a distinct class in $\Ext(P_{m+1}^V,P_{m+1})$.
\end{lemma}
\begin{proof}
  Given a nontrivial direct sum decomposition $V=U\oplus W$, we may identify $U=V/W$ and $W=V/U$ to get the following commutative diagram:
  \[\xymatrix{ & & 0 \ar[d] & 0 \ar[d] & \\
    & & P_m\otimes U \ar@{=}[r]\ar[d] & P_m\otimes(V/W) \ar[d] & \\
    0 \ar[r] & P_m\otimes W \ar@{=}[d]\ar[r] & P_{m+1}\ar[r]\ar[d]\ar@{}[dr]|(.7){\lrcorner} & P_{m+1}^W \ar[d]\ar[r] & 0 \\
    0 \ar[r] & P_m\otimes(V/U) \ar[r] & P_{m+1}^U \ar[r]\ar[d] & P_{m+1}^V \ar[r]\ar[d] & 0\\
    & & 0 & 0 & }\]
  Since the left vertical morphism (or upper horizontal morphism) is an equality, the lower right square is a pullback.
  It follows that the sequence
  \[\xymatrix{0 \ar[r] & P_{m+1} \ar[r] & P_{m+1}^U\oplus P_{m+1}^W \ar[r] & P_{m+1}^V}\]
  is exact.
  But the morphism $P_{m+1}^U\oplus P_{m+1}^W\to P_{m+1}^V$ is clearly surjective and thus we obtain an element of $\Ext(P_{m+1}^V,P_{m+1})$.

@@

For $V\in Gr(H_m)$, $m\ge1$, any subspace $W\subset V$ gives rise to an exact sequence
\[\xymatrix{0 \ar[r] & P_m\otimes(V/W) \ar[r]^(.6){ev} & P_{m+1}^W \ar[r] & P_{m+1}^V \ar[r] & 0},\]
where the left hand morphism above is the natural evaluation morphism coming from Lemma~\ref{le:truncated homomorphisms}.
Each such sequence has the following almost-split property for proper subrepresentations of $P_{m+1}^V$.
\begin{lemma}
  For $V\in Gr(H_m)$, $m\ge1$, given any proper subrepresentation $X\subsetneq P_{m+1}^V$, the upper pullback sequence
  \[\xymatrix{0 \ar[r] & P_m\otimes(V/W) \ar@{=}[d]\ar[r] & Y\ar[r] \ar[d]\ar@{}[dr]|(.7){\lrcorner} & X \ar[d]\ar[r] & 0 \\
    0 \ar[r] & P_m\otimes(V/W) \ar[r] & P_{m+1}^W \ar[r] & P_{m+1}^V \ar[r] & 0}\]
  splits for every proper subspace $W\subsetneq V$.
\end{lemma}
\begin{proof}
  We proceed by induction on $\codim_V W$.  
  When $\codim_V W=1$, we have an exact sequence
  \[\xymatrix{0 \ar[r] & P_m\otimes(V/W) \ar[r] & P_{m+1}^W \ar[r] & P_{m+1}^V \ar[r] & 0}\] 
  with both morphisms irreducible by Lemma~\ref{le:irreducible morphisms} and the claim immediately follows.

  Suppose $W\subsetneq V$ with $\codim_V W>1$ and choose an intermediate subspace $W\subsetneq T\subsetneq V$.
  Given $X\subsetneq P_{m+1}^V$, we have the pullback diagram
  \[\xymatrix{ Y \ar[d]\ar[r]\ar@{}[dr]|(.7){\lrcorner} & Y'\ar[r]\ar[d]\ar@{}[dr]|(.7){\lrcorner} & X \ar[d]\\
  P_{m+1}^W \ar[r] & P_{m+1}^T \ar[r] & P_{m+1}^V}\]
  in which all horizontal morphisms of the upper row are split epimorphisms by induction.
  The result now follows since the outer square is also a pullback.
\end{proof}

>>>>

\noindent Denote by $K(n)$ the \emph{$n$-Kronecker quiver} $1\stackrel{n}{\longleftarrow}2$ with vertices $K_0(n)=\{1,2\}$ and $n$ arrows from vertex $2$ to vertex $1$. 
Write $\Sigma_1$ and $\Sigma_2$ for the BGP-reflection functors of $K(n)$ \cite{bgp}. 
Note that (up to relabeling vertices) the quiver $K(n)$ itself does not change when applying the reflection functors and thus we view them as endofunctors acting on the category $\rep K(n)$ of finite-dimensional representations. %, but the vertices $1$ and $2$ are exchanged. 
With this identification of $K(n)$ and $K(n)^{op}$, the endofunctors $\Sigma_1\Sigma_2$ and $\Sigma_2\Sigma_1$ are each naturally isomorphic to the identity.
Also, following \cite{brenner-butler}, the Auslander-Reiten translation $\tau:\rep K(n)\to\rep K(n)$ may be identified with the functor $\Sigma_1^2$.

Define Chebyshev polynomials $u_k$ for $k\in\ZZ$ by the recursion $u_0=0$, $u_1=1$, $u_{k+1}=nu_k-u_{k-1}$.
\begin{theorem}
  For each $m\ge1$, there exist unique (up to isomorphism) indecomposable rigid representations $P_m$ and $I_m$ of $K(n)$ with dimension vectors $(u_m,u_{m-1})$ and $(u_{m-1},u_m)$ respectively. 
  Moreover, any rigid representation of $K(n)$ is isomorphic to one of the form $P_m^{a_1}\oplus P_{m+1}^{a_2}$ or $I_m^{a_1}\oplus I_{m+1}^{a_2}$ for some $m\ge1$ and some $a_1,a_2\ge0$.
\end{theorem}
The representations $P_m$ are called the \emph{preprojective} representations of $K(n)$ and the representations $I_m$ are called \emph{preinjective}.
\begin{remark}
  \label{rem:reflection recursion}
  These representations satisfy the following recursions using the reflection functors:
  \[P_1=S_1,\quad P_m=\Sigma_2 P_{m-1},\quad I_1=S_2,\quad I_m=\Sigma_1 I_{m-1}\]
  for $m\ge2$.
  In particular, we have $P_{m-1}=\tau P_{m+1}$ and $I_{m+1}=\tau I_{m-1}$ for $m\ge2$. 
\end{remark}

@@

%\begin{lemma}
%  For any $m\ge1$, we have 
%  \[\dim\Hom(P_m,P_m)=1,\quad \dim\Hom(P_m,P_{m+1})=n,\quad \dim\Hom(P_{m+1},P_m)=0, \quad\dim\Ext(P_{m+1},P_m)=0.\]  
%  Moreover, for $1\le k<n$ and linearly independent functions $f_1,\ldots,f_k\in\Hom(P_m,P_{m+1})$, the map $[f_1\ \cdots\ f_k]:P_m^k\to P_{m+1}$ is injective. 
%\end{lemma}
%\begin{proof} 
%  Note that we have an Auslander-Reiten sequence
%  \begin{equation}
%    \label{eq:AR sequence}
%    0\longrightarrow P_{m-1}\stackrel{\iota_{m-1}}{\longrightarrow} P_m^n\stackrel{[f_1\ \cdots\ f_n]}{\longrightarrow} P_{m+1}\longrightarrow 0
%  \end{equation}
%  with irreducible homomorphisms $f_i$ which are also linearly independent. 
%  Thus they do not factor through a representation $Z\neq P_{m}$ which already means that they are injective, see for instance \cite[Lemma 1.6]{ass}. 
%  If we pick $k<n$ linearly independent homomorphisms $f_{i_1},\ldots, f_{i_k}$, this also means that $[f_{i_1}\ \cdots\ f_{i_k}]:P_m^k\to P_{m+1}$ is injective. 
%  Indeed otherwise, at least one of the homomorphisms would be forced to factor through a representation $Z\neq P_{m}$.
%\end{proof}
%\begin{remark}
%  Fix a basis $\{f_{m,1},\ldots,f_{m,n}\}$ for $\Hom(P_m,P_{m+1})$, $m\ge2$.
%  Define a basis $\{f_{\ell,1},\ldots,f_{\ell,n}\}$ for each $\Hom(P_\ell,P_{\ell+1})$, $1\le\ell\le m-1$, by downward induction as follows.  
%  Write $\iota_\ell:P_\ell\to P_{\ell+1}^n$ for the left-hand morphism from the sequence \eqref{eq:AR sequence} computed using $f_k=f_{\ell+1,k}$, $1\le k\le n$. 
%  Then the basis element $f_{\ell,k}$ is given by composing $\iota_\ell$ with the coordinate projection $\pi_k:P_{\ell+1}^n\to P_{\ell+1}$ onto the $k$-th factor.
%  Indeed, applying $\Hom(-,P_{\ell+1})$ to this sequence \eqref{eq:AR sequence} gives an isomorphism $\Hom(P_{\ell+1}^n,P_{\ell+1})\cong\Hom(P_\ell,P_{\ell+1})$ whereby the natural basis of coordinate projections on the left is taken to the basis $\{f_{\ell,k}\}$ on the right.
%\end{remark}
\begin{corollary}
  \label{cor:preprojective homomorphism duality}
  The sequence \eqref{eq:AR sequence} gives rise to an isomorphism $H_m^*\cong H_{m-1}$.
\end{corollary}
\begin{proof}
  Define a map $H_m^*\to H_{m-1}$ by $\varphi\mapsto\bar{\varphi}:=(id\overline{\otimes}\varphi)\circ\iota_{m-1}$, in words $\bar{\varphi}$ acts on $x\in P_{m-1}$ by contracting with the second factor in $\iota_{m-1}(x)$ to give an element of $P_m$.
  Suppose $\varphi\in H_m^*$ is a nonzero functional on $H_m$ and let $V\subsetneq H_m$ denote the kernel of $\varphi$.
  Then $\bar{\varphi}=0\in H_{m-1}$ if and only if the image of $\iota_{m-1}$ is contained in $P_m\otimes V\subsetneq P_m\otimes H_m$.
  But then Lemma~\ref{le:injective evaluation maps} implies $\iota_{m-1}$ is the zero map, a contradiction.
  Thus the map $H_m^*\to H_{m-1}$, $\varphi\mapsto\bar{\varphi}$ must be injective and hence an isomorphism.
\begin{remark}
  The set $Gr(H_m)$ is naturally a poset and Corollary~\ref{cor:preprojective homomorphism duality} gives an identification of the opposite poset $Gr(H_m)^{op}\cong Gr(H_m^*)$ with $Gr(H_{m-1})$.
  We write $\bar{V}\subset H_{m-1}$ for the subspace corresponding to $V\subset H_m$ under this identification.
  Under the isomorphism of $H_{m-1}$ with $H_m^*$, we have $\bar{V}=(H_m/V)^*$.
\end{remark}
Following Remark~\ref{rem:reflection recursion}, the reflection functor $\Sigma_1$ provides a natural identification of $H_m$ with $H_{m-1}$ for $m\ge2$. 
Combining with Corollary~\ref{cor:preprojective homomorphism duality} we obtain a natural isomorphism $H_m^*\cong H_m$ for $m\ge2$.
The next observation is essential for the results to follow.
\begin{proposition}
  For $V\in Gr(H_m)$, $m\ge1$, we have $\bar{\bar{V}}=\tau V$.
\end{proposition}
\begin{proof}
  We show that $\bar{\bar{\varphi}}=\tau\varphi$ for $\varphi\in H_m$.
  Indeed, we have
  \[\bar{\bar{\varphi}}=(id\overline{\otimes}\bar{\varphi})\circ\iota_{m-2}=\Big(id\overline{\otimes}\big((id\overline{\otimes}\varphi)\circ\iota_{m-1}\big)\Big)\circ\iota_{m-2}.\]

@@

\begin{lemma}
  \label{le:unique truncated extension}
  For $V\in Gr(H_m)$, $m\ge2$, the space $\Ext(P_{m+1}^V,P_{m-1})$ is one-dimensional and spanned by the extension
  \begin{equation}
    \label{eq:unique extension}
    \xymatrix{0 \ar[r] & P_{m-1} \ar[r]^(.375){\kappa_V} & P_m\otimes(H_m/V) \ar[r] & P_{m+1}^V \ar[r] & 0}.
  \end{equation}
\end{lemma}
\begin{proof}
  Applying the functor $\Hom(-,P_{m-1})$ to the sequence \eqref{eq:truncated preprojectives} gives an isomorphism $\Ext(P_{m+1}^V,P_{m-1})\cong\Ext(P_{m+1},P_{m-1})$ with a one-dimensional space.
  Writing $X$ for the unique extension of $P_{m+1}^V$ by $P_{m-1}$, this isomorphism gives rise to the following pullback diagram:
  \[\xymatrix{ & & 0 \ar[d] & 0\ar[d] & \\
    & & P_m\otimes V \ar@{=}[r]\ar[d] & P_m\otimes V\ar[d] & \\
    0 \ar[r] & P_{m-1} \ar@{=}[d]\ar[r]^(.425){\iota_{m-1}} & P_m\otimes H_m \ar[r]\ar[d]\ar@{}[dr]|(.7){\lrcorner} & P_{m+1} \ar[r]\ar[d] & 0\\
    0 \ar[r] & P_{m-1} \ar[r]^{\kappa_V} & X \ar[r]\ar[d] & P_{m+1}^V \ar[r]\ar[d] & 0\\
    & & 0 & 0 & }\]
  from which we immediately obtain the isomorphism $X\cong P_m\otimes(H_m/V)$.
\end{proof}
\begin{corollary}
  \label{cor:truncated preprojective isomorphism}
  Suppose $V\in Gr(H_m)$ has codimension one in $H_m$.  Then $P_{m+1}^V\cong P_m^{\bar{V}}$.
\end{corollary}
\begin{proof}
  By Lemma~\ref{le:unique truncated extension}, we have the exact sequence
  \[\xymatrix{0 \ar[r] & P_{m-1} \ar[r]^(.35){\kappa_V} & P_m\otimes(H_m/V) \ar[r] & P_{m+1}^V \ar[r] & 0}.\]
  But $H_m/V$ is a one-dimensional vector space and so $P_m\otimes(H_m/V)\cong P_m$.
  Under this identification, the left hand morphism $\kappa_V$ in the sequence above identifies with a generator of $\bar{V}$ and thus $P_{m+1}^V\cong P_m^{\bar{V}}$.
\end{proof}
\begin{corollary}
  For $V,W\in Gr(H_m)$, $m\ge3$, the space $\Ext(P_{m+1}^V,P_{m-1}^{\bar{\bar{W}}})$ has dimension 0 or 1.. .
\end{corollary}

@@

  Applying the functor $\Hom(-,P_m^{\bar{W}})$ to the sequence \eqref{eq:AR sequence} we get an exact sequence 
  \[\xymatrix{0 \ar[r] & \Hom(P_{m+1},P_m^{\bar{W}}) \ar[r] & \Hom(P_m\otimes H_m,P_m^{\bar{W}}) \ar[r] & \Hom(P_{m-1},P_m^{\bar{W}}) \ar[r] & 0}.\]
  By Lemma~\ref{le:basic homological properties}, the middle space above is isomorphic to $H_m^*$ and thus $\Hom(P_{m+1},P_m^{\bar{W}})$ can be identified with the kernel of the natural map $H_m^*\to W^*$, i.e.\ with the space $(H_m/W)^*$.
\end{proof}
\begin{remark}
  For $W\in Gr(H_m)$, $m\ge2$, a nonzero element $\varphi\in\Hom(P_{m+1},P_m^{\bar{W}})=(H_m/W)^*$ corresponds, by taking the kernel of $\varphi$, to a codimension 1 subspace $V\subset H_m$ containing $W$.
  Then the map $\varphi$ is (up to scalars) the composition of the natural projection $\pi_V:P_{m+1}\to P_{m+1}^V$, the isomorphism $P_{m+1}^V\cong P_m^{\bar{V}}$ from Corollary~\ref{cor:truncated preprojective isomorphism}, and the unique projection $P_m^{\bar{V}}\to P_m^{\bar{W}}$.
\end{remark}
\begin{corollary}
  For $V,W\in Gr(H_m)$, $m\ge2$, we have natural isomorphisms 
  \[\Hom(P_{m+1}^V,P_m^{\bar{W}})\cong\big(H_m/(V+W)\big)^*\quad\text{and}\quad\Ext(P_{m+1}^V,P_m^{\bar{W}})\cong(V\cap W)^*.\]
\end{corollary}
\begin{proof}
  Applying the functor $\Hom(-,P_m^{\bar{W}})$ to the sequence \eqref{eq:truncated preprojectives} we get an exact sequence
  \[\xymatrix{0 \ar[r] & \Hom(P_{m+1}^V,P_m^{\bar{W}}) \ar[r] & \Hom(P_{m+1},P_m^{\bar{W}}) \ar[r] & \Hom(P_m\otimes V,P_m^{\bar{W}}) \ar[r] & \Ext(P_{m+1}^V,P_m^{\bar{W}}) \ar[r] & 0}.\]
  By Lemma~\ref{le:more truncated homomorphisms}, we may identify $\Hom(P_{m+1}^V,P_m^{\bar{W}})$ and $\Ext(P_{m+1}^V,P_m^{\bar{W}})$ with the kernel and cokernel of the natural map $(H_m/W)^*\to V^*$.
  The result immediately follows from this.
\end{proof}
\begin{remark}
  It is slightly easier to understand the dual of the diagram figuring in the proof above, in particular it is immediate that the kernel of the natural morphism $V\to H_m/W$ is $V\cap W$ while the cokernel of this morphism is $H_m/(V+W)$.
\end{remark}

\begin{lemma}
  For $V,W\in Gr(H_m)$, $m\ge2$, with $\dim W=1$, we have $\Hom(P_{m+1}^V,P_{m-1}^{\bar{\bar{W}}})\cong\big(H_m/(V+W)\big)^*$.
\end{lemma}

\begin{lemma}
  For $m\ge2$ and $V\in Gr(H_m)$, the Auslander-Reiten translate of the truncated preprojective $P_{m+1}^V$ is again a truncated preprojective representation of $K(n)$.  More precisely, we have $\tau(P_{m+1}^V)=P_{m-1}^{\bar{\bar{V}}}$.
\end{lemma}
\begin{proof}
  Under the Auslander-Reiten translation, the subspace $V\subset H_m$ is taken to a subspace $\tilde V\subset H_{m-2}$ of the same dimension.
  It follows that the evaluation morphism $P_m\otimes V\stackrel{ev_V}{\longrightarrow} P_{m+1}$ transforms via $\tau$ to the evaluation morphism $P_{m-2}\otimes\tilde V\stackrel{ev_{\tilde V}}{\longrightarrow} P_{m-1}$.
  Thus the sequence \eqref{eq:truncated preprojectives} transforms via $\tau$ to the exact sequence
  \[0\longrightarrow P_{m-2}\otimes \tilde V\stackrel{ev_{\tilde V}}{\longrightarrow} P_{m-1}\stackrel{\pi_{\tilde V}}{\longrightarrow} P_{m-1}^{\tilde V}\longrightarrow 0.\]
  This proves the first claim.

@@

\begin{lemma}
  \label{le:truncated exact sequences}
  For $V\in Gr(H_m)$, $m\ge2$, each nontrivial direct sum decomposition $V=U\oplus W$ gives rise to an exact sequence
  \[\xymatrix{0 \ar[r] & P_{m+1} \ar[r] & P_{m+1}^U\oplus P_{m+1}^W \ar[r] & P_{m+1}^V \ar[r] & 0}\]
  representing a distinct class in $\Ext(P_{m+1}^V,P_{m+1})$.
\end{lemma}
\begin{proof}
  Given a nontrivial direct sum decomposition $V=U\oplus W$, we may identify $U=V/W$ and $W=V/U$ to get the following commutative diagram:
  \[\xymatrix{ & & 0 \ar[d] & 0 \ar[d] & \\
    & & P_m\otimes U \ar@{=}[r]\ar[d] & P_m\otimes(V/W) \ar[d] & \\
    0 \ar[r] & P_m\otimes W \ar@{=}[d]\ar[r] & P_{m+1} \ar[r]\ar[d]\ar@{}[dr]|(.7){\lrcorner} & P_{m+1}^W \ar[d]\ar[r] & 0 \\
    0 \ar[r] & P_m\otimes(V/U) \ar[r] & P_{m+1}^U \ar[r]\ar[d] & P_{m+1}^V \ar[r]\ar[d] & 0\\
    & & 0 & 0 & }\]
  Since the left vertical morphism (or upper horizontal morphism) is an equality, the lower right square is a pullback.
  It follows that the sequence
  \[\xymatrix{0 \ar[r] & P_{m+1} \ar[r] & P_{m+1}^U\oplus P_{m+1}^W \ar[r] & P_{m+1}^V}\]
  is exact.
  But the morphism $P_{m+1}^U\oplus P_{m+1}^W\to P_{m+1}^V$ is clearly surjective and thus we obtain an element of $\Ext(P_{m+1}^V,P_{m+1})$.

@@

For $V\in Gr(H_m)$, $m\ge1$, any subspace $W\subset V$ gives rise to an exact sequence
\[\xymatrix{0 \ar[r] & P_m\otimes(V/W) \ar[r]^(.6){ev} & P_{m+1}^W \ar[r] & P_{m+1}^V \ar[r] & 0},\]
where the left hand morphism above is the natural evaluation morphism coming from Lemma~\ref{le:truncated homomorphisms}.
Each such sequence has the following almost-split property for proper subrepresentations of $P_{m+1}^V$.
\begin{lemma}
  For $V\in Gr(H_m)$, $m\ge1$, given any proper subrepresentation $X\subsetneq P_{m+1}^V$, the upper pullback sequence
  \[\xymatrix{0 \ar[r] & P_m\otimes(V/W) \ar@{=}[d]\ar[r] & Y \ar[r]\ar[d]\ar@{}[dr]|(.7){\lrcorner} & X \ar[d]\ar[r] & 0 \\
    0 \ar[r] & P_m\otimes(V/W) \ar[r] & P_{m+1}^W \ar[r] & P_{m+1}^V \ar[r] & 0}\]
  splits for every proper subspace $W\subsetneq V$.
\end{lemma}
\begin{proof}
  We proceed by induction on $\codim_V W$.  
  When $\codim_V W=1$, we have an exact sequence
  \[\xymatrix{0 \ar[r] & P_m\otimes(V/W) \ar[r] & P_{m+1}^W \ar[r] & P_{m+1}^V \ar[r] & 0}\] 
  with both morphisms irreducible by Lemma~\ref{le:irreducible morphisms} and the claim immediately follows.
